Case Study: scRNA-seq (Human data, MAST method)

### 2018-04-03 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Add cellular detection rate to MAST model

We apply MAST to the TPMs following the approach in Soneson et al.

```{r, MAST}
# function to add MAST p-values
compute_MAST_sc <- function(dat){
  # check if already computed
  if (! "mast_p" %in% colnames(rowData(dat))){
    sca <- FromMatrix(exprsArray = log2(assay(dat, "TPM") + 1), 
                    cData = data.frame(wellKey=colnames(dat), colData(dat)))
    zlmdata <- zlm(~group, sca)

>>>>

We apply MAST to the TPMs and adjust for the cellular detection rate, as 
suggested by the authors of MAST in the manuscript and vignette on Bioconductor.

```{r, MAST}
# function to add MAST p-values
compute_MAST_sc <- function(dat){
  # check if already computed
  if (! "mast_p" %in% colnames(rowData(dat))){
    sca <- FromMatrix(exprsArray = log2(assay(dat, "TPM") + 1), 
                    cData = data.frame(wellKey=colnames(dat), colData(dat)))
    colData(sca)$cdr <- scale(colSums(assay(sca)>0))
    zlmdata <- zlm(~ group + cdr, sca)
